Towards a Machine Learning approach for Aggregate Computing

### 2021-11-04 paper-2021-woa-ac-ml.tex
on background

\newcommand{\unibo}{\textsc{Alma Mater Studiorum} -- \textit{Università di Bologna}}
\newcommand{\disi}{\textit{Computer Science and Engineering - DISI}}
\newcommand{\scafi}{{ScaFi}}
\newcommand{\scalaloci}{{ScalaLoci}}
\newcommand{\scafiloci}{{ScaFiLoci}}
\newcommand{\scalainline}[1]{\mintinline[fontsize=\small]{scala}{#1}}
%%%%% LEGENDA FOR NOTES %%%%%
%% RED: constraints
%% YELLOW: suggestions
%% CYAN: todos
%% GREEN: outline
\newcommand{\constraints}[1]{\todo[inline, color=red]{#1}}
\newcommand{\suggestions}[1]{\todo[inline, color=yellow]{#1}}
\newcommand{\todos}[1]{\todo[inline, color=cyan]{#1}}
\newcommand{\outline}[1]{\todo[inline, color=green]{#1}}
%% Utility commands
\newcommand{\hybridaggregate}{\textit{Hybrid Aggregate Computing}}
\newcommand{\round}{\texttt{round}}
\newcommand{\export}{\texttt{export}}

@@

\suggestions{Perhaps we could change the narration directly towards "reinforcement learning". I think that I cannot continue to explore multiple solutions..}
\section{Introduction}
Nowadays, computer engineers have to deal with Collective Adaptive Systems (CASs)
 due to the increasing interconnected computational devices placed in ever-changing environments.
 Examples of those include robot swarm, smart cities and augmenting crowds.

@@

So, we claim that Machine Learning can help us in handling this "unseen" situation, leaving only the burden
 to developers of defining the right collective specifications.
%
This lead to an ``hybrid" approach where a part of behaviour is still expressed using common 
 Aggregate Computing abstractions and another part is distilled through learning~\cite{research}.
%
In this paper, as the first steps towards a so-called \hybridaggregate{}, we investigate how Aggregate Computing can be
 extended with Reinforcement Learning through a case
 study where we outline the performance improvement of the "hop count" program.
\suggestions{If we leave the part about "roadmap" and "machine learning similar setting", we need to add some description here.}
\suggestions{I do not know if we can avoid it altogether, but also a brief description of machine learning approaches can be useful in the paper flow}

\section{Background and Related Work}
\outline{Probably, for a "short" paper, this section can be avoided.}
\outline{walkthrogh traditional engineering way to design CAS}
\outline{walkthrogh Aggregate Computing}
\subsection{Field calcus}
\todos{I think it can be helpful to introduce fields calculus through ScaFi...}
\subsection{Machine Learning}
\suggestions{I do not know, perhaps it is better to avoid this }
\outline{walkthrogh Machine learning approach applied in MARL}
\outline{current limitation (application-specific, not large scale, centralised in some cases,..)}

>>>>

\newcommand{\unibo}{\textsc{Alma Mater Studiorum} -- \textit{Università di Bologna}}
\newcommand{\disi}{\textit{Computer Science and Engineering - DISI}}
\newcommand{\scafi}{{ScaFi}}
\newcommand{\scalaloci}{{ScalaLoci}}
\newcommand{\scafiloci}{{ScaFiLoci}}
\newcommand{\scalainline}[1]{\mintinline[fontsize=\small]{scala}{#1}}
%%%%% LEGENDA FOR NOTES %%%%%
%% RED: constraints
%% YELLOW: suggestions
%% CYAN: todos
%% GREEN: outline
\newcommand{\constraints}[1]{\todo[inline, color=red]{#1}}
\newcommand{\suggestions}[1]{\todo[inline, color=yellow]{#1}}
\newcommand{\todos}[1]{\todo[inline, color=cyan]{\textbf{TODO}: #1}}
\newcommand{\outline}[1]{\todo[inline, color=green]{#1}}
%% Utility commands
\newcommand{\hybridaggregate}{\textit{Hybrid Aggregate Computing}}
\newcommand{\round}{\texttt{round}}
\newcommand{\export}{\texttt{export}}

@@

\section{Introduction}
Nowadays, computer engineers have to deal with Collective Adaptive Systems (CASs)
 due to the increasing interconnected computational devices placed in ever-changing environments.
 Examples of those include robot swarm, smart cities and augmenting crowds.

@@

So, we claim that Machine Learning can help us in handling this "unseen" situation, leaving only the burden
 to developers of defining the right collective specifications.
%
This lead to an ``hybrid" approach where a part of behaviour is still expressed using common 
 Aggregate Computing abstractions and another part is distilled through learning~\cite{research}.
%
In this paper, as the first steps towards a so-called \hybridaggregate{}, we investigate how Aggregate Computing can be
 extended with Reinforcement Learning through a case
 study where we outline the performance improvement of the "hop count" program.
\todos{Outline}
\suggestions{I do not know if we can avoid it altogether, but also a brief description of machine learning approaches can be useful in the paper flow}

\section{Background and Related Work}

Computer Science is an incredibly evolving research area. 
 In a few years, the environment had been filled with intercommunicating computational devices, such as smartphones, smart things, and personal computers.

In particular, in literature, we speak of Collective Adaptive Systems
 when the number is incredibly high, there is no central authority that coordinate nodes,
 the overall behaviour is reached with local interactions, the systems expose self-* properties,
 and the ensemble pursuit of collective goals
 exhibiting swarm intelligence.

\outline{Probably, for a "short" paper, this section can be avoided.}
\outline{walkthrogh traditional engineering way to design CAS}
\outline{walkthrogh Aggregate Computing}
\subsection{Field calcus}
\todos{I think it can be helpful to introduce fields calculus through ScaFi...}
\subsection{Machine Learning}
\suggestions{I do not know, perhaps it is better to avoid this }
\outline{walkthrogh Machine learning approach applied in MARL}
\outline{current limitation (application-specific, not large scale, centralised in some cases,..)}
